\begin{thebibliography}{99}

%\addcontentsline{toc}{chapter}{Bibliography}

\bibitem{SPOTLIGHT}
Apple Spotlight, \emph{http://developer.apple.com/macosx/spotlight.html}

\bibitem{GOOGLEDESKTOP}
Google Desktop Search, \emph{http://googledesktop.blogspot.in}

\bibitem{SEMSURVEY} 
Mangold.C, \emph{A survey and classification of semantic search approaches}, 
Int. J. Metadata, Semantics and Ontology, Vol. 2, No. 1, Page(s): 23-34.

\bibitem{STAT2011}  %used
Gopal.S, Yang.Y, Salomatin.K, Carbonell.J, 
\emph{Statistical Learning for File-Type Identification}, 
2011 10th International Conference on Machine Learning and Applications, Page(s): 68-73.

\bibitem{TAGFS} %used
Bloehdorn.S, Grlitz.O, Schenk.S, Vlkel.M, 
\emph{TagFS - Tag Semantics for Hierarchical File Systems},
In Proceedings of the 6th International Conference on Knowledge Management (I-KNOW 06), Graz, Austria, September 6-8, 2006.

\bibitem{SEMFS} %in literature survey
Gifford.D, Jouvelot.P, Sheldon.M, and O’Toole.J, \emph{Sematic File Systems}. 
13th ACM Symposium on Operating Systems Principles, ACM Operating Systems Review, October, 1991, Page(s): 16-25.

\bibitem{NHFS} %in literature survey
Freund.R, 
\emph{File Systems and Usability — the Missing Link},
Cognitive Science, University of Osnabruck July 2007.

\bibitem{TAGSISTANT} %in literature survey
Tagsistant, 
\emph{http://www.tagsistant.net}

\bibitem{TAGSTER} %in literature survey
Tagster, 
\emph{http://www.uni-koblenz.de}

\bibitem{KFS}
Chang.K, Perdana.I, Jain.M, Kartasasmita.I, Ramadhana.B, Sethuraman.K, Le.T, Chachra.N, Tikale.S, 
\emph{Knowledge File System-A principled approach to personal information management},
2010 IEEE International Conference on Data Mining Workshops, Page(s): 1037-1044.

\bibitem{SMFS2011}
Eck.O, Schaefer.D, 
\emph{A semantic file system for integrated product data management}, 2011 Advanced Engineering Informatics, Page(s): 177-184.

\bibitem{VIRDIR}
Mohan.P, Venkateswaran.S, Raghuraman, Dr. Siromoney.A, 
\emph{Semantic File Retrieval in File Systems using Virtual Directories},
Proc. Linux Expo Conference, Raleigh, NC, May 2007, Page(s): 141-151.

\bibitem{MiningAssoc}
Rakesh.A, Tomasz.I, Arun.S, 
\emph{Mining Association Rules between Sets of Items in Large Databases}, SIGMOD Conference 1993, Page(s): 207-216.

\bibitem{STMGMTSYS}
Schroder.A, Fritzsche.R, Schmidt.S, Mitschick.A, Meißner.K, 
\emph{Semantic Extension of a Hierarchical Storage Management System for Small and Medium-sized Enterprises}.
Proceedings of the 1st International Workshop on Semantic Digital Archives (SDA 2011).

\bibitem{SMO2012}
Hua.Y, Jiang.H, Zhu.Y, Feng.D, Tian.L,
\emph{Semantic-Aware Metadata Organization Paradigm in Next-Generation File Systems}, 
IEEE Transactions On Parallel And Distributed Systems, 
Vol. 23, No. 2, February 2012, Page(s): 337-344.

%%technologies used
\bibitem{FUSE}
File system in USERspace (FUSE) homepage and documentation, 
\emph{http://fuse.sourceforge.net}

\bibitem{SQLITE}
SQLite database, 
\emph{http://www.sqlite.org}
%%end of technologies used

\bibitem{FastAlgo}
Rakesh. A, Ramakrishnan. S, 
\emph{Fast algorithms for mining association rules in large databases},
Proceedings of the 20th International Conference on Very Large Data Bases, VLDB, Santiago, Chile, September 1994, Page(s): 487-499.

\end{thebibliography}
